Check Coverage

### 2019-07-05 analysis/coverage_check.Rmd
Excluded data without trait matches to get complete dataset.

check if all bird & mammal biotime data w/id's has an elton match. There are 63 species without a match (54 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, matchingName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

Get data w/traits for all studies that have >85% trait coverage
```{r}
#set coverage threshold for analysis dataset
perc <- 0.85

@@

biotime_traits_list <- map2(taxa, traits, ~merge_data(taxa = .x, trait_data = .y))
coverage <- map_dfr(biotime_traits_list, get_coverage) %>%
  filter(perc > perc)

biotime_traits <- biotime_traits_list %>%
  bind_rows() %>%
  filter(study_id %in% coverage$study_id)
```

>>>>

check if all bird & mammal biotime data w/id's has an elton match. There are 63 species without a match (54 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, sourceName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

Get data w/traits for all studies that have >85% trait coverage
```{r}
#set coverage threshold for analysis dataset
percent <- 0.85

@@

biotime_traits_list <- map2(taxa, traits, ~merge_data(taxa = .x, trait_data = .y))
coverage <- map_dfr(biotime_traits_list, get_coverage) %>%
  filter(perc > percent)

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  #bind_rows() %>%
  filter(study_id %in% coverage$study_id)
```
